### 2020-09-01 benchmarking/benchmarkingVM/ESS_round4b.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:18
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(474.88,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,186.05) --
	( 54.10,174.62);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 54.10,180.33) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,164.25) --
	( 60.20,141.62);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 60.20,152.94) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,167.28) --
	( 66.29,150.64);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 66.29,158.96) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,166.76) --
	( 72.39,144.26);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 72.39,155.51) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,162.02) --
	( 78.49, 98.30);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 78.49,130.16) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,202.23) --
	( 84.59,189.46);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 84.59,195.84) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,203.28) --
	( 90.69,181.04);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 90.69,192.16) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,240.71) --
	( 96.79,222.93);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 96.79,231.82) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,176.33) --
	(102.88,176.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {1.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
	(108.98,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,192.84) --
	(115.08,179.45);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (115.08,186.14) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,182.97) --
	(121.18,171.24);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (121.18,177.11) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,184.85) --
	(127.28,171.12);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (127.28,177.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,190.36) --
	(133.38,166.22);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (133.38,178.29) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,169.54) --
	(139.47,147.07);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (139.47,158.31) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,195.26) --
	(145.57,186.84);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (145.57,191.05) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,257.34) --
	(151.67,213.88);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (151.67,235.61) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,242.16) --
	(157.77,219.28);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (157.77,230.72) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,193.08) --
	(163.87,193.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {7.4\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
	(169.97,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,183.40) --
	(176.06,181.91);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.06,182.66) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,178.32) --
	(182.16,176.29);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (182.16,177.30) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,173.36) --
	(188.26,171.68);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (188.26,172.52) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,167.30) --
	(194.36,164.77);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (194.36,166.03) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,175.58) --
	(200.46,173.46);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (200.46,174.52) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,188.62) --
	(206.56,187.01);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (206.56,187.82) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,191.38) --
	(212.65,187.66);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (212.65,189.52) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,221.94) --
	(218.75,219.83);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (218.75,220.89) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,184.37) --
	(224.85,184.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {4.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
	(230.95,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,181.65) --
	(237.05,172.54);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.05,177.10) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,159.01) --
	(243.15,132.62);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (243.15,145.81) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,177.17) --
	(249.24,157.93);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (249.24,167.55) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,189.97) --
	(255.34,147.35);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (255.34,168.66) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,177.18) --
	(261.44,164.80);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (261.44,170.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,208.69) --
	(267.54,185.32);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (267.54,197.01) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,218.20) --
	(273.64,198.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (273.64,208.22) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,223.20) --
	(279.74,214.78);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (279.74,218.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,182.72) --
	(285.83,182.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {3.5\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
	(291.93,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,178.61) --
	(298.03,167.68);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.03,173.15) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,162.68) --
	(304.13,139.42);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (304.13,151.05) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,176.48) --
	(310.23,158.35);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (310.23,167.41) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,195.13) --
	(316.33,158.87);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (316.33,177.00) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,176.14) --
	(322.42,165.55);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (322.42,170.84) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,208.50) --
	(328.52,185.79);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (328.52,197.14) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,224.16) --
	(334.62,192.88);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (334.62,208.52) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,226.54) --
	(340.72,218.12);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (340.72,222.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,184.32) --
	(346.82,184.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {4.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
	(352.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,182.24) --
	(359.01,167.41);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.01,174.82) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,157.24) --
	(365.11,131.60);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (365.11,144.42) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,169.99) --
	(371.21,153.88);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (371.21,161.94) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,168.23) --
	(377.31,146.43);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (377.31,157.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,174.11) --
	(383.41,150.84);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (383.41,162.48) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,193.90) --
	(389.51,166.47);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (389.51,180.18) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:41
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(476.29,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,175.23) --
	( 53.56,146.36);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 53.56,160.80) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,186.05) --
	( 59.12,174.62);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 59.12,180.33) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,164.25) --
	( 64.69,141.62);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 64.69,152.94) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,167.28) --
	( 70.25,150.64);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 70.25,158.96) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,179.53) --
	( 75.81,164.10);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 75.81,171.82) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,162.02) --
	( 81.37, 98.30);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 81.37,130.16) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,202.23) --
	( 86.94,189.46);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 86.94,195.84) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,203.28) --
	( 92.50,181.04);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 92.50,192.16) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,240.71) --
	( 98.06,222.93);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] ( 98.06,231.82) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,176.39) --
	(103.62,176.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {1.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
	(109.18,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,200.32) --
	(114.75,179.86);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (114.75,190.09) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,192.84) --
	(120.31,179.45);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (120.31,186.14) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,182.97) --
	(125.87,171.24);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (125.87,177.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,184.85) --
	(131.43,171.12);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (131.43,177.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,184.14) --
	(137.00,167.55);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (137.00,175.84) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,169.54) --
	(142.56,147.07);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (142.56,158.31) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,195.26) --
	(148.12,186.84);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (148.12,191.05) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,257.34) --
	(153.68,213.88);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (153.68,235.61) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,242.16) --
	(159.24,219.28);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (159.24,230.72) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,192.50) --
	(164.81,192.50);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {7.2\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
	(170.37,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,178.18) --
	(175.93,171.14);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (175.93,174.66) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,183.40) --
	(181.49,181.91);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (181.49,182.66) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,178.32) --
	(187.05,176.29);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (187.05,177.30) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,173.36) --
	(192.62,171.68);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (192.62,172.52) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,173.13) --
	(198.18,167.55);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (198.18,170.34) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,175.58) --
	(203.74,173.46);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (203.74,174.52) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,188.62) --
	(209.30,187.01);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (209.30,187.82) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,191.38) --
	(214.87,187.66);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (214.87,189.52) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,221.94) --
	(220.43,219.83);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (220.43,220.89) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,183.76) --
	(225.99,183.76);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {3.9\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
	(231.55,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,175.10) --
	(237.11,147.62);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.11,161.36) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,181.65) --
	(242.68,172.54);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (242.68,177.10) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,159.01) --
	(248.24,132.62);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (248.24,145.81) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,177.17) --
	(253.80,157.93);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (253.80,167.55) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,184.40) --
	(259.36,154.83);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (259.36,169.62) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,177.18) --
	(264.93,164.80);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (264.93,170.99) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,208.69) --
	(270.49,185.32);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (270.49,197.01) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,218.20) --
	(276.05,198.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (276.05,208.22) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,223.20) --
	(281.61,214.78);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (281.61,218.99) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,180.53) --
	(287.17,180.53);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {2.7\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
	(292.74,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,171.47) --
	(298.30,146.80);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.30,159.14) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,178.61) --
	(303.86,167.68);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (303.86,173.15) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,162.68) --
	(309.42,139.42);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (309.42,151.05) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,176.48) --
	(314.99,158.35);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (314.99,167.41) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,197.57) --
	(320.55,164.96);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (320.55,181.26) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,176.14) --
	(326.11,165.55);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (326.11,170.84) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,208.50) --
	(331.67,185.79);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (331.67,197.14) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,224.16) --
	(337.23,192.88);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (337.23,208.52) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,226.54) --
	(342.80,218.12);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (342.80,222.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,182.10) --
	(348.36,182.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {3.2\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
	(353.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,183.45) --
	(359.48,166.61);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.48,175.03) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}
